Efficient and Scalable Bipartite Matching with Fast Beta Linkage (fabl)

### 2021-10-12 methods_paper/fabl-paper.tex
moved bk computational complexity to proof.

\newtheorem*{remark}{Remark}
\newtheorem{proposition}{Proposition}
\newtheorem*{definition}{Definition}

@@

\hypertarget{computational-complexity}{%
	\subsection{Computational Complexity}\label{computational-complexity}}

{
\color{blue}
The computational complexity of \texttt{fabl} is determined by its two steps: constructing comparison vectors and Gibbs sampling. The computational complexity of all pairwise comparisons across files $\mathbf{X}_1$ and $\mathbf{X}_2$ is $O(F n_1 n_2)$. Since \texttt{fabl} is able to compute these comparisons in parallel, we can split these computations across $B$ equally sized partitions, so the complexity becomes $O(\frac{F}{B} n_1 n_2)$.

Without hashing, the computational complexity of updating the $\mathbf{m}$ and $\mathbf{u}$ parameters is $O(F n_1 n_2)$. However, by doing calculations over the agreement patterns rather than the individual record, hashing reduces the complexity to $O(FP)$.

The complexity of updating $Z$ sequentially at the record level is $O(n_1 n_2)$. With hashing, we split this sampling into two steps; first we sample that agreement pattern of the match with complexity $O(n_2 P)$, and then we sample the record that exhibits that pattern with complexity $O(n_2)$. Thus we have reduced the complexity of the Gibbs sampler under \texttt{BRL} from $O(F n_1 n_2)$ to $O(n_2 P)$.

Overall, the computational complexity under the complete \texttt{fabl} framework is $O(\frac{F}{B} n_1 n_2) + O(n_2 P)$.
}

>>>>

\newtheorem*{remark}{Remark}
\newtheorem{proposition}{Proposition}
\newtheorem*{definition}{Definition}
\newtheorem*{lemma}{Lemma}

@@

\hypertarget{computational-complexity}{%
	\subsection{Computational Complexity}\label{computational-complexity}}
In this section, we provide the computational complexity of \texttt{fabl} in Lemma \ref{lemma:fabl}.

\newpage
\begin{lemma}
The overall computational complexity of \texttt{fabl} is $O(\frac{F}{B} n_1 n_2) + O(n_2 P).$
\end{lemma}

\begin{proof}
To prove the computational complexity, we consider two steps --- constructing the comparison vectors and the Gibbs sampler. 
%
The computational complexity of all pairwise comparisons across the two databases $\mathbf{X}_1$ and $\mathbf{X}_2$ is $O(F n_1 n_2)$. Since \texttt{fabl} is able to compute these comparisons in parallel, we can split these computations across $B$ equally sized partitions, so the complexity becomes $O(\frac{F}{B} n_1 n_2)$.\footnote{Without hashing, the computational complexity of updating the $\mathbf{m}$ and $\mathbf{u}$ parameters is $O(F n_1 n_2)$. However, by doing calculations over the agreement patterns rather than the individual record, hashing reduces the overall complexity to $O(FP)$, where $F$ is the total number of features and $P$ is the total number of agreement patterns.}
The complexity of updating $Z$ sequentially at the record level is $O(n_1 n_2)$. With hashing, we split this sampling into two steps. First we sample that agreement pattern of the match with complexity $O(n_2 P).$ Next,  we sample the record that exhibits that pattern with complexity $O(n_2)$. Thus we have reduced the complexity of the Gibbs sampler (under \texttt{BRL})from $O(F n_1 n_2)$ to $O(n_2 P)$.
In summary, the total computational complexity is $O(\frac{F}{B} n_1 n_2) + O(n_2 P).$
\end{proof}

%{
%\color{blue}
%The computational complexity of \texttt{fabl} is determined by its two steps: constructing comparison vectors and Gibbs sampling. The computational complexity of all pairwise comparisons across files $\mathbf{X}_1$ and $\mathbf{X}_2$ is $O(F n_1 n_2)$. Since \texttt{fabl} is able to compute these comparisons in parallel, we can split these computations across $B$ equally sized partitions, so the complexity becomes $O(\frac{F}{B} n_1 n_2)$.
%
%Without hashing, the computational complexity of updating the $\mathbf{m}$ and $\mathbf{u}$ parameters is $O(F n_1 n_2)$. However, by doing calculations over the agreement patterns rather than the individual record, hashing reduces the complexity to $O(FP)$.
%
%The complexity of updating $Z$ sequentially at the record level is $O(n_1 n_2)$. With hashing, we split this sampling into two steps; first we sample that agreement pattern of the match with complexity $O(n_2 P)$, and then we sample the record that exhibits that pattern with complexity $O(n_2)$. Thus we have reduced the complexity of the Gibbs sampler under \texttt{BRL} from $O(F n_1 n_2)$ to $O(n_2 P)$.
%
%Overall, the computational complexity under the complete \texttt{fabl} framework is $O(\frac{F}{B} n_1 n_2) + O(n_2 P)$.
%}
